07_summary_stats

### 2023-11-21 07_summary_stats.Rmd
Update 07_summary_stats.Rmd

```{r fig.width=12}
###### Buoy 8 ####
W.08 <- GPSwhaleAISenvSS08 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "PM")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS08, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 8: TOL 125 Plot + PM'))
g2 <- plotPresGrid(W.08, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS08$UTC),
                         end = max(GPSwhaleAISenvSS08$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS08, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 8: TOL 2000 Plot + PM')
t2 <- plotPresGrid(W.08, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS08$UTC),
                         end = max(GPSwhaleAISenvSS08$UTC), fill = NA, color = "white")

@@

W.10 <- GPSwhaleAISenvSS10 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "PM")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS10, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 10: TOL 125 Plot + PM'))
g2 <- plotPresGrid(W.10, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS10$UTC),
                         end = max(GPSwhaleAISenvSS10$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS10, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 10: TOL 2000 Plot + PM')
t2 <- plotPresGrid(W.10, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS10$UTC),
                         end = max(GPSwhaleAISenvSS10$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
## Buoy 20
W.20 <- GPSwhaleAISenvSS20 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS20, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 20: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.20, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS20$UTC),
                         end = max(GPSwhaleAISenvSS20$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS20, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 20: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.20, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS20$UTC),
                         end = max(GPSwhaleAISenvSS20$UTC), fill = NA, color = "white")

@@

W.20 <- GPSwhaleAISenvSS20 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "ZC")

W.20plot <- plotPresGrid(W.20, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS20$UTC),
                         end = max(GPSwhaleAISenvSS20$UTC),  by = 'Wpresence', alpha = 0.5)

plotTimeseries(GPSwhaleAISenvSS20, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 20: TOL 2000 Plot') +  W.20plot
plotTimeseries(GPSwhaleAISenvSS20, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 20: TOL 125 Plot') +  W.20plot

>>>>

```{r fig.width=12}
###### Buoy 8 ####
W.08 <- GPSwhaleAISenvSS08 %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS08, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 8: TOL 125 Plot + zC'))
g2 <- plotPresGrid(W.08, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS08$UTC),
                         end = max(GPSwhaleAISenvSS08$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS08, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 8: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.08, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS08$UTC),
                         end = max(GPSwhaleAISenvSS08$UTC), fill = NA, color = "white")

@@

@@

g1 <- (plotTimeseries(GPSwhaleAISenvSS10, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 10: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.10, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS10$UTC),
                         end = max(GPSwhaleAISenvSS10$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISenvSS10, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 10: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.10, bin = 'hour', type = 'presence', start = min(GPSwhaleAISenvSS10$UTC),
                         end = max(GPSwhaleAISenvSS10$UTC), fill = NA, color = "white")

@@

```{r fig.width=12}
# Read in buoy 20 without environmental variables
GPSwhaleAISSS20.alt <- readRDS("D:/Buoy_dfs/GPSwhaleAISSS20_alt.rda")

## Buoy 20
W.20 <- GPSwhaleAISSS20.alt %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "ZC")

@@

g1 <- (plotTimeseries(GPSwhaleAISSS20.alt, column='TOL_125', bin='1hour', 
                      style = 'heatmap', title='Buoy 20: TOL 125 Plot + ZC'))
g2 <- plotPresGrid(W.20, bin = 'hour', type = 'presence', start = min(GPSwhaleAISSS20.alt$UTC),
                         end = max(GPSwhaleAISSS20.alt$UTC), fill = NA, color = "white")

combined.g <- g1
combined.g$layers <- c(combined.g$layers, g2$layers)
#####
t1 <- plotTimeseries(GPSwhaleAISSS20.alt, column='TOL_2000', bin='1hour', 
                     style = 'heatmap', title='Buoy 20: TOL 2000 Plot + ZC')
t2 <- plotPresGrid(W.20, bin = 'hour', type = 'presence', start = min(GPSwhaleAISSS20.alt$UTC),
                         end = max(GPSwhaleAISSS20.alt$UTC), fill = NA, color = "white")

@@

W.20 <- GPSwhaleAISSS20.alt %>%
  select(UTC, Wpresence, species) %>%
  filter(species == "ZC")

W.20plot <- plotPresGrid(W.20, bin = 'hour', type = 'presence', start = min(GPSwhaleAISSS20.alt$UTC),
                         end = max(GPSwhaleAISSS20.alt$UTC),  by = 'Wpresence', alpha = 0.5)

plotTimeseries(GPSwhaleAISSS20.alt, column='TOL_2000', bin='1hour', style = 'heatmap', title='Buoy 20: TOL 2000 Plot') +  W.20plot
plotTimeseries(GPSwhaleAISSS20.alt, column='TOL_125', bin='1hour', style = 'heatmap', title='Buoy 20: TOL 125 Plot') +  W.20plot
